### 2009-04-06 talk/icooolps2009-dotnet/benchmarks.tex
Typo.

\item \textbf{Dynamic lookup}: attributes and methods are looked up at
  runtime, because there is no way to know in advance if and where an object
  have that particular attribute or method.
\end{itemize}

>>>>

\item \textbf{Dynamic lookup}: attributes and methods are looked up at
  runtime, because there is no way to know in advance if and where an object
  has that particular attribute or method.
\end{itemize}
